%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jacob Colvin 06/2023 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper,hidelinks]{altacv}

%Layout
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

%Packages
\usepackage{paracol}
\usepackage{gensymb}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

%Colors
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{GoldenEarth}{HTML}{E7D192}
\definecolor{VividPurple}{HTML}{3E0097}

\colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{subheading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{black}
\colorlet{body}{SlateGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\newcommand{\cveventinv}[4]{%
  {\large\color{emphasis}#1\par}
  \smallskip\normalsize
  \ifstrequal{#2}{}{}{
  \textbf{\color{accent}#2}\par
  \smallskip}
  \ifstrequal{#4}{}{}{{\small\color{emphasis}\makebox[0.25\linewidth][l]{\faMapMarker~#4}}}%
  \ifstrequal{#3}{}{}{{\small\color{emphasis}\makebox[0.25\linewidth][l]{\faCalendar~#3}}}\par
  \medskip\normalsize
}

\newcommand{\cvsubevent}[2]{%
    {\small\color{body}\makebox[0.5\linewidth][l]{#1}%
    {\makebox[0.5\linewidth][l]{\color{body}\faCalendar\hspace{0.5em}#2}}\par}
    \smallskip
}

\newcommand{\cvproject}[3]{%
    \textbf{\small\color{accent}\makebox[0.5\linewidth][l]{#1}}%
    {\makebox[0.5\linewidth][l]{\small\color{emphasis}#3\hspace{0.5em}{#2}}}\par
    \medskip
}

%

\begin{document}
\name{Jacob Colvin}
\tagline{Site Reliability \& Platform Engineer}
%\photo{2.5cm}{}
\personalinfo{%
  \location{Cincinnati, Ohio}
  \email{me@jacobcolvin.com}
  \homepage{jacobcolvin.com}
  \twitter{@0xMacro}
  \linkedin{colvinjm}
  \github{MacroPower}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% About %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{About}

\small{I enjoy writing software and creating platforms that make my and other developers' lives easier. I am passionate about open source software and observability, and thrive on simplifying the complexities that arrive with distributed architectures. In my free time, I am an avid homelabber, gamer, audiophile, and mechanical keyboard collector. Below are some areas of interest and expertise:}

\medskip
\smallskip

%\textcolor{emphasis}{Certifications:}\smallskip
%\cvachievement{\faTrophy}{Fantastic Achievement}{and some details about it}
%\medskip
%\smallskip

\textcolor{emphasis}{Development:}\smallskip

\cvtag{Go / Golang}
\cvtag{Python}
\cvtag{FastAPI}
\cvtag{C\#}
\cvtag{TypeScript / JavaScript}
\cvtag{React}
\cvtag{Vue}
\cvtag{Jsonnet}
\cvtag{Terraform}
\cvtag{Ansible}
\par
\cvtag{pprof / Profiling}
\cvtag{OpenTelemetry}
\cvtag{PowerShell}
\cvtag{Bash}
\cvtag{Make}

\medskip
\smallskip

\textcolor{emphasis}{Operations:}\smallskip

\cvtag{Kubernetes - AKS, k3s}
\cvtag{Helm}
\cvtag{Azure}
\cvtag{Docker}
\cvtag{Crossplane}
\cvtag{FluxCD}
\cvtag{ArgoCD}
\cvtag{GitHub Actions}
\cvtag{Cloud Foundry}
\cvtag{Databricks}
\cvtag{Postgres}
\cvtag{Prometheus}
\cvtag{Thanos}
\cvtag{Grafana}
\cvtag{Jaeger}
\cvtag{Fluentd}
\cvtag{Telegraf}
\cvtag{Datadog}

\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}

\cveventinv{Senior Site Reliability Engineer}{84.51\degree / Kroger}{April 2021 -- Current}{Remote / Cincinnati, Ohio}

\begin{itemize}
    \item   \small{Led development of multiple Prometheus exporters using Go, utilizing Redis for caching, distributed workers with pub/sub and leader election, CEL for custom rule evaluation, Cue and custom tooling for validation, and Go text templating.}
    \item   \small{Developed Python library to centralize instrumentation for metrics (OpenMetrics), tracing (OTEL), logging, and profiling (pprof), with support for the FastAPI framework, Databricks notebooks, and more.}
    \item   \small{Rolled out Datadog as a unified logging platform for both Azure and on-premises systems, using Terraform for configuration and Fluentd for log parsing and forwarding.}
    \item   \small{Deployed and supported enterprise observability services/tooling, both on-premises (Ansible) and in Azure Kubernetes (Flux), \par including Grafana, Prometheus, Thanos, Fluentd, Telegraf, and Jaeger.}
    \item   \small{Contributed small fixes to Grafana, Thanos, Jaeger, and other upstream repos.}
\end{itemize}

\medskip\divider

\cveventinv{Versatilist / Site Reliability Engineer}{84.51\degree / Kroger}{December 2019 -- April 2021}{Cincinnati, Ohio}

\begin{itemize}
    \item   \small{Created and administered multiple Azure environments using Terraform in Azure DevOps, which included solutions such as \par Databricks, Datafactory, Key Vaults, Storage Accounts, Postgres Databases, and more.}
    \item   \small{Assisted a multitude of development/data teams with observability, cloud, CI/CD, and fulfilled other ad-hoc requests as needed.}
    \item   \small{Enhanced our Prometheus ecosystem by adding high-availability and long-term storage via Thanos, thus allowing consumers of Prometheus to track SLOs and KPIs over years instead of days.}
\end{itemize}

\divider

\cveventinv{IT Intern / Co-op}{84.51\degree / Kroger}{May 2016 -- December 2019}{Cincinnati, Ohio}

\begin{itemize}
    \item   \small{Designed a C\# API layer over several legacy systems, and a SPA using TypeScript with React, to assist with support, data \par automation, and tech deprecation.}
    \item   \small{Created a C\# Prometheus exporter for SonarQube data, along with corresponding dashboards, rules and alerts, to allow security team to gather KPIs.}
    \item   \small{Automated Red Hat Linux VM deployment through ServiceNow, via interactions with Satellite, vCenter, SolarWinds and Ansible.}
    \item   \small{Designed a custom web framework using PowerShell and Bootstrap for executing administrative tasks and aggregating events and metrics from many distinct products.}
    \item   \small{Created and documented Automic workflows with Bash and SAS ODS.}
    \item   \small{Automated many miscellaneous tasks using PowerShell, VBA, Bash and PL/SQL in Bash.}
    \item   \small{Interfaced with BOSH and Hadoop to design custom Pivotal Cloud Foundry (PCF) monitoring solution.}
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Soft-skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Soft-skills}

% \cvtag{Flexibility}
% \cvtag{Responsibility}
% \cvtag{Multitasking}
% \cvtag{Context switching}
% \cvtag{Agile}
% \cvtag{Teamwork}



%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Key Projects}

\cvproject{OmegaGraf}{\href{https://jacobcolvin.com/OmegaGraf}{jacobcolvin.com/OmegaGraf}}{\faGlobe}

\begin{itemize}
    \item   \small{An open-source project that seeks to completely automate vCenter monitoring, by orchestrating a small ecosystem of containers, including Telegraf, Prometheus, and Grafana.}
    \item   \small{Paper: \url{https://scholar.uc.edu/concern/student\_works/jw827c971}}
    \item   \small{Technologies: Docker, C\# / .NET Core, TypeScript, React}
\end{itemize}

\medskip\divider

\cvproject{Homelab}{\href{https://github.com/MacroPower/homelab}{MacroPower/homelab}}{\faGithub}

\begin{itemize}
    \item   \small{Infrastructure-as-code for my homelab / personal cloud. Defines multi-cluster k3s-on-MicroOS, spanning across bare metal and multiple \par Hetzner cloud environments.}
    \item   \small{Technologies: k3s, Linkerd, ArgoCD, Helm, Jsonnet, Terraform}
\end{itemize}

\medskip\divider

\cvproject{Prometheus Video Renderer}{\href{https://github.com/MacroPower/prometheus\_video\_renderer}{MacroPower/prometheus\_video\_renderer}}{\faGithub}

\begin{itemize}
    \item   \small{Just for fun, completely impractical tool that allows you to encode \par media as Prometheus metrics.}
    \item   \small{Featured on the Grafana blog: \url{https://grafana.com/blog/2021/07/30/how-to-use-grafana-and-prometheus-to-rickroll-your-friends-or-enemies}}
    \item   \small{Technologies: Go, Jsonnet}
\end{itemize}

\medskip\divider

\cvproject{Analytics Panel Plugin}{\href{https://github.com/MacroPower/macropower-analytics-panel}{MacroPower/macropower-analytics-panel}}{\faGithub}

\begin{itemize}
    \item   \small{Grafana panel that injects JavaScript which reports user session \par information to a backend Go server, which exposes Prometheus metrics.}
    \item   \small{Over 800k downloads, featured by Giant Swarm: \url{https://www.giantswarm.io/blog/grafana-ception-or-how-we-do-grafana-analytics-giant-swarm}}
    \item   \small{Technologies: TypeScript, React, Go}
\end{itemize}

\medskip\divider

\cvproject{Wakatime Exporter}{\href{https://github.com/MacroPower/wakatime\_exporter}{MacroPower/wakatime\_exporter}}{\faGithub}

\begin{itemize}
    \item   \small{Prometheus exporter and Grafana dashboards for Wakatime coding statistics.}
    \item   \small{Over 100k downloads}
    \item   \small{Technologies: Go}
\end{itemize}

\switchcolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Education}

\cvevent{B.S.\ Information Technology}{University of Cincinnati - CECH}{Aug 2015 -- April 2020}{}

\begin{itemize}
    \setlength{\itemindent}{0em}
    \item   \small{Cybersecurity specialization}
    \item   \small{Summa Cum Laude}
\end{itemize}

\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Coding Time %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \cvsection{Coding Time}
 
 \small{Past Year}

 \wheelchart{1.5cm}{0.5cm}{%
   40/2em/accent!60/Go,
   40/2em/accent!40/Python,
   5/2em/accent!10/Jsonnet,
   3/15em/accent!40/Terraform,
   20/2em/accent!30/Other
}

\end{paracol}

\end{document}
